---
title: "Surveys"
editor_options: 
  chunk_output_type: console
---

## 2023-03-20: Kickoff Survey 

* [**Survey** of Priorities for Biodiversity Indicators MarineBON.org Working Group](https://docs.google.com/forms/d/e/1FAIpQLScUmZszSqUv2ER6lc8xFl-a8Lwn8OpA16LHoTHBYkcdWgQIIw/viewform)
* [**Priorities** for MBON Biodiversity Indicators Working Group - Google Docs](https://docs.google.com/document/d/1Njq1BCFeByJEJUhvVC6PxcF20uKOrGWb8xNG2yh-vdI/edit#heading=h.1w03je9uy705)

```{r}
librarian::shelf(
  dplyr, DT, glue, purrr, readr, stringr, tidyr)

survey_csv <- "https://docs.google.com/spreadsheets/d/1xohI010hAwtbSyLpOr1-oFG5-W3ASiRC8EmHrDjNa0k/export?format=csv&gid=1947036924"

d <- read_csv(survey_csv, col_types = "c") |> 
  rename(email = `Your email? (optional)`)

n_respondents <- nrow(d)
emails <- d |> 
  filter(!is.na(email)) |> 
  arrange(email) |> 
  pull(email)

cols <- colnames(d)
qs <- cols |>
  str_subset("\\[") |> 
  str_split_i(" \\[", 1) |> 
  unique()
d_cols_other <- tibble(
  col      = cols |> 
    str_subset("What other"),
  question = col |> 
    str_replace("\n"," ") |> 
    str_replace(".*(What other .*)","\\1"),
  q        = question |> 
    str_replace("What other ([a-z]+) .*", "\\1") |> 
    str_to_sentence())
col2q = setNames(d_cols_other$q, d_cols_other$col)
d_other <- d |> 
  select(all_of(c("email", d_cols_other$col))) |> 
  pivot_longer(
    !email,
    names_to  = "col",
    values_to = "comment",
    values_drop_na = T) |> 
  mutate(
    q = recode(col, !!!col2q)) |> 
  arrange(q, email)

get_question <- function(q){
  d_cols_other |> 
    filter(q == !!q) |> 
    pull(question)
}

get_comments <- function(q){
  # DEBUG: q="General"
  d_other |> 
    filter(q == !!q) |> 
    select(respondent = email, comment) |> 
    replace_na(
      list(respondent = "anonymous")) |> 
    mutate(
      md = glue("
        1. {respondent}  
          {comment}")) |> 
    pull(md) |> 
    paste(collapse = "\n")
}

summarize_q <- function(q, d){
  # DEBUG: q = "Regions"
  d_q <- d |> 
    select(starts_with(q)) |> 
    pivot_longer(
      everything(),
      names_to  = "option",
      values_to = "val_str",
      values_drop_na = T) |> 
    mutate(
      option  = str_replace(
        option |> str_replace("\n",""), 
        ".*\\[(.*)\\]", "\\1"),
      val_int = recode(
        val_str,
        "1. Critical"          = 3L,
        "2. Important"         = 2L,
        "3. Desirable"         = 1L,
        "4. Least Interesting" = -1L)) |> 
    group_by(option) |> 
    summarise(
      score_avg = mean(val_int)) |> 
    arrange(desc(score_avg), option)
}

d_q <- tibble(
  q    = qs |> str_split_i("\n", 1),
  data = map(q, summarize_q, d)) |> 
  unnest(data)
# setdiff(d_q$q, unique(d_other$q)) # Audience

dt_q <- function(q){
  d_q |> 
    filter(q == !!q) |> 
    select(Option = option, Score = score_avg) |> 
    datatable(
      options = list(pageLength = 10)) |> 
    formatRound(columns=c('Score'), digits=2)
}
```


::: {.callout-note collapse="true"}
## Respondents & Scoring

::::: {.columns}

::::::: {.column width="50%"}

### Respondents

n_respondents: **`r n_respondents`**

Emails:

1. `r paste(emails, collapse = "\n1. ")`
1. n_anonymous: `r n_respondents - length(emails)`

:::::::

::::::: {.column width="50%"}

### Scoring

- `3`: Critical
- `2`: Important
- `1`: Desirable
- `-1`: Least Interesting

Note: blanks are not counted in average.

:::::::

:::::

:::

::: {.panel-tabset}

### Indicators

```{r}
dt_q("Indicators")
```

`r get_question("Indicators")`

`r get_comments("Indicators")`


### Regions

Regions of interest, ie spatial analytical units to generate time series of indicators

```{r}
dt_q("Regions")
```

`r get_question("Regions")`

`r get_comments("Regions")`


### Products

```{r}
dt_q("Products")
```

`r get_question("Products")`

`r get_comments("Products")`


### Audience

Audience for whom are we generating these indicators and products

```{r}
dt_q("Audience")
```

`r get_question("Audience")`

`r get_comments("Audience")`


### Industries

```{r}
dt_q("Industries")
```

`r get_question("Industries")`

`r get_comments("Industries")`


### Initiatives

```{r}
dt_q("Initiatives")
```

`r get_question("Initiatives")`

`r get_comments("Initiatives")`


### Partners

```{r}
dt_q("Partners")
```

`r get_question("Partners")`

`r get_comments("Partners")`


### Data

Observational and attribute data to use for developing indicators

```{r}
dt_q("Data")
```

`r get_question("Data")`

`r get_comments("Data")`


### Portals

Portals to distribute indicators

```{r}
dt_q("Portals")
```

`r get_question("Portals")`

`r get_comments("Portals")`


:::

